### 2019-09-01 reports/thesis/chapters/2_dataCollection.tex

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector. The target material in the x-ray tube is tungsten. The detector is made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produce a projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}. Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$. The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects. The gain and offset were adjusted by the engineers to produce a projection with good contrast and with negligible penumbra effect. Each pixel has a grey value in units of analogue to digital units (\SI{}{\adu}).

>>>>

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner (\emph{Nikon Metrology, UK}) together with a \emph{Perkin Elmer XRD 1621 (Perkin Elmer, US)} detector. The target material in the x-ray tube is tungsten. The detector is made up of 2 rows and 16 columns of panels and together has dimensions of $\SI{409.6}{\milli\metre}\times\SI{409.6}{\milli\metre}$ which produce a 16-bit projection of $\SI{2048}{\pixel}\times\SI{2048}{\pixel}$ in size \citep{perkinelmer2006xrd}. Therefore the scale of each pixel is $\SI{200.0}{\micro\metre\per\pixel}$. The projections were cropped to $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ to remove boundary effects. The gain and offset were adjusted by the engineers to produce a projection with good contrast and with negligible penumbra effect. Each pixel has a grey value in units of analogue to digital units (\SI{}{\adu}).
